On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-10 manuscripts/IEEE/final_submission.tex
edits

\begin{corollary}\label{ProbabilisticCor}
If indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
\end{corollary}

>>>>

\begin{corollary}\label{ProbabilisticCor}
If the indeterminate entries of $\mathbf{A}$ and the $\mathbf{x}_i$ are drawn independently from probability distributions absolutely continuous with respect to the standard Borel measure, then $Y$ has a stable $k$-sparse representation in $\mathbb{R}^m$ with probability one.
\end{corollary}
